### 2021-09-06 input/figproofB.tex
wip rw up to broadcast
cosmetic + number
first step in styling
meow
starting on three-phase purge

\begin{tikzpicture}[scale=0.87]

@@

  \newcommand\X{85pt}
  \newcommand\Y{-50pt}

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}

@@

@@

  \draw[<->] (5pt - \X, 0.4*\Y) --
  node[below, font=\small]{\textbf{I': propagation}}
  (-5pt, 0.4*\Y); %% I as well

  \draw[->] (-\X + 5pt, 0)
  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_d \rightarrow$}
  -- (0 - 5pt, 0)
  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{d \neq f}$}
  ; %% d - e

  \draw[<->] (5pt , 0.4*\Y) --
  node[below, font=\small]{\textbf{III: detection}}
  (-5pt + \X, 0.4*\Y); %% IV

  \draw[->] (0 +5pt, 0)
  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PH}{\ADD_h^{z'}} \rightarrow$}
  --
  (\X -5pt, 0)
  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_h \not\rightarrow \ADD_h^{z'}}$}
  ; %% e - f

  \draw[<->] (5pt +\X , 0.4*\Y) --
  node[below, font=\small]{\textbf{IV: propagation}}
  (-5pt + 2*\X, 0.4*\Y); %% V

@@

  \draw[fill=white] (-\X, 0) node{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PH]{$\bm{e}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node[color=\PD]{$\bm{f}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node[color=\PD]{$\bm{g}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-\X, 5pt) node[above]{$\textcolor{\PD}{\ADD_d} \rightarrow \DEL_d$};

  \draw ( 0, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PC}{\ADD_d^{\vphantom{z'}}}]{\mbox{\scriptsize{before}}}
    \xrightarrow[\textcolor{\PH}{\ADD_h^{z\vphantom{'}}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_h^{\vphantom{z'}} ]{\mbox{\scriptsize{expect}}}$};

  \draw ( \X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PH}{\ADD_h^{\vphantom{y'}}} \rightarrow \DEL_h]{\mbox{\scriptsize{before}}}
    \xrightarrow[\textcolor{\PC}{\ADD_d^{y'}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_d^{\vphantom{z'}}?]{\mbox{\scriptsize{expect}}}$};

  \draw (2*\X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PC}{\ADD_d^{y''}}]{\mbox{\scriptsize{last}}}
    \xrightarrow[\DEL_d^{\vphantom{y'}}?]{\mbox{\scriptsize{expect}}}$};

@@

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y) node[below right, font=\scriptsize]{somewhere: $\textcolor{\PH}{\ADD_h} \rightarrow \DEL_h$};

>>>>

\begin{tikzpicture}[scale=0.9]

@@

  \newcommand\X{115pt}
  \newcommand\Y{-60pt}

  \newcommand\ADD{\alpha}
  \newcommand\DEL{\delta}
  \newcommand\DELDEL{\Delta}

@@

  \draw[dotted] (-1.5*\X, 0pt) -- (-1.35*\X, 0pt); %% X ->

@@

  \draw[<->] (5pt - \X, 0.4*\Y) --
  node[below, font=\small, align=center]{\textbf{I: propagation}\\\textbf{of $\delta$ messages}}
  (-5pt, 0.4*\Y); %% I as well

  \draw[->] (-\X + 5pt, 0)
  node[below=-0.3em, below right, font=\scriptsize]{$\DEL_X \rightarrow$}
  -- (0 - 5pt, 0)
  node [below=-0.15em, below left, font=\tiny]{$\textcolor{\WRONG}{a \neq c}$}
  ; %% d - e

  \draw[<->] (5pt , 0.4*\Y) --
  node[below, font=\small, align=center]{\textbf{II: detection}}
  (-5pt + \X, 0.4*\Y); %% IV

  \draw[->] (0 +5pt, 0)
  node[below=-0.3em, below right, font=\tiny]{$\textcolor{\PY}{\ADD_Y^{y'}} \rightarrow$}
  --
  (\X -5pt, 0)
  node [left= -0.15em, below=-0.3em, below left, font=\tiny]{$\textcolor{\WRONG}{\DEL_Y^{\vphantom{y'}} \not\rightarrow \ADD_Y^{y'}}$}
  ; %% e - f

  \draw[<->] (5pt +\X , 0.4*\Y) --
  node[below, font=\small, align=center]{\textbf{III: propagation}\\\textbf{of $\DELDEL$ messages}}
  (-5pt + 2*\X, 0.4*\Y); %% V

@@

  \draw[dotted] (0.5*\X, 1.25*\Y) -- (0.2*\X, 1.1*\Y); %% Y ->
  \draw[dotted] (0.5*\X, 1.25*\Y) -- (0.8*\X, 1.1*\Y); %% Y ->

  \draw[fill=white] (-1.5*\X, 0) node{$\bm{X}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (-\X, 0) node{$\bm{a}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);  
  \draw[fill=white] (0, 0) node[color=\PY]{$\bm{b}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (\X, 0) node[color=\PX]{$\bm{c}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (2*\X, 0) node[color=\PX]{$\bm{d}$} +(-5pt, -5pt) rectangle +(5pt, 5pt);
  \draw[fill=white] (0.5*\X, 1.25*\Y)node{$\bm{Y}$}+(-5pt, -5pt) rectangle +(5pt, 5pt);

  \draw (-1.5*\X, 5pt) node[above]{$\textcolor{\PX}{\ADD_X} \rightarrow \DEL_X$};

  \draw (-\X, 5pt) node[above, font=\tiny]{$\textcolor{\PX}{\ADD_X} \rightarrow \DEL_X$};

  \draw ( 0, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PX}{\ADD_X^{\vphantom{x'}}}]{\mbox{\tiny{before}}}
    \xrightarrow[\textcolor{\PY}{\ADD_Y^{y\vphantom{'}}}]{\mbox{\tiny{last}}}
    \xrightarrow[\DEL_Y^{\vphantom{y'}} ]{\mbox{\tiny{expect}}}$};

  \draw ( \X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PY}{\ADD_Y^{\vphantom{y'}}} \rightarrow
      \DEL_Y^{\vphantom{y'}}]{\mbox{\tiny{before}}}
    \xrightarrow[\textcolor{\PX}{\ADD_X^{x'}}]{\mbox{\tiny{last}}}
    \xrightarrow[\DELDEL_X^{\vphantom{y'}}]{\mbox{\tiny{expect}}}$};

  \draw (2*\X, 5pt) node[above, font=\footnotesize]{$
    \xrightarrow[\textcolor{\PX}{\ADD_X^{x''}}]{\mbox{\tiny{last}}}
    \xrightarrow[\DELDEL_X^{\vphantom{x'}}]{\mbox{\tiny{expect}}}$};

  \draw (0.5*\X, 1.25*\Y+5pt) node[above] {$\textcolor{\PY}{\ADD_Y} \rightarrow \DEL_Y$};

@@

  \draw[->] ( 0,  0.5*\Y) -- ( 0, -5pt);
  \draw[dotted] ( 0,  0.5*\Y) -- ( 0, 0.9*\Y);

### 2021-09-06 input/proposal.tex
starting on three-phase purge

\begin{theorem}[\label{theo:dcp}BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When a \process can \texttt{Add} and \texttt{Del}ete its partition,
consistent partitioning additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item then best eventual forwarding so such an $m'$ ends up
  originating from the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:]
    %% also transiting messages
    Assuming that every \process removes control information as soon as
    it becomes stale ($S(\alpha_a^x) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then BEF:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \processes eventually
    delivers and forwards the best up-to-date delivered
    messages. \Processes reach consistent partitioning together.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
\end{proof}

%% \begin{figure}
%%   \centering\input{input/figproofA.tex}
%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
%%       stop other $\alpha$ messages from reaching all \processes ($b$
%%       and $c$) that require it along the shortest path. Consistent
%%       partitioning requires eventual purging of stale messages (see
%%       Figure~\ref{fig:proofB}).}
%% \end{figure}

\TODO{The challenge is therefore about purging.}

One could guarantee consistent partitioning by always propagating the
$\delta$ messages corresponding to the $\alpha$ messages it propagated
before. In Figure~\ref{fig:problem}, it means that as soon as
\Process~$b$ forwards $\alpha_a^2$, it assumes that its neighbors
\Process~$c$ and \Process~$d$ may need the notification of removal
$\delta_a$ if it exists. However, such a solution also implies that
\processes generate traffic not only related to their current
partition, but also related to partitions they belonged to in the
past. This would prove overly expensive in dynamic systems where
\processes join and leave the system, create and delete partitions, at
any time.  Instead, we propose to use the delivery order at each
\process to detect possible inconsistencies and solve them. Together,
\processes eventually remove all stale control information (transiting
messages and local states) of the system leaving room for propagation
of messages about up-to-date partitions.

@@

\begin{theorem}[Three-phase purge] % Propagations $+$ detection $\implies$ purge]
  Purging stale control information from its source to every \process
  that may have delivered it last requires three
  phases:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possible blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

\begin{figure}
  \centering\input{input/figproofB.tex}
  \caption{\label{fig:proofB}Stale $\alpha$ messages may
      stop $\delta$ messages from reaching \processes with the corresponding
      partition. Consistent partitioning requires that all \processes propagate
      $\delta$ messages as often as possible (I'); detect possible inconsistencies
      when parents' $\alpha$ messages contradict history or state (III); notify
      \processes of possible inconsistencies (IV)}
\end{figure}

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[d, e, f, g]$ delivered
  and forwarded a message $\alpha_d$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_d$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_d$:] \Processes such as
    \Process~$d$ where the last and best partition is still $P_d$. By
    propagating from \process to \process the corresponding $\delta_d$
    message, these \processes purge $\alpha_d$.
  \item [\processes with $\alpha_d^y \rightarrow \alpha_h^z$ with last
    $\alpha_h^z$, for $\alpha_h^z < \alpha_d^y$:] \Processes such as
    \Process~$e$ that do not directly suffer from the non-delivery of
    $\delta_d$. They need to purge their own $P_h$ if need
    be. Nonetheless, they deliver and forward $\alpha_h$ that at least
    one following \process will receive.
  \item [\processes with $\delta_h \rightarrow \alpha_d$:] \Processes
    such as \Process~$f$ that do not belong to the preceding category,
    for they already delivered $\delta_h$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_h$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_d$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\delta_d?$ to emphasize
    the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_d$ receiving $\delta_d?$ from
    their parent:] \Processes such as \Process~$g$ that have
    $\alpha_d$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\delta_d?$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

@@

This vector of versions constitutes a summary of deliveries. \NAME
uses it to detect possible inconsistent partitioning as depicted in
Figure~\ref{fig:proofB}. A detecting \process then propagates a
$\delta$ message conveying the unique identifier $s$ and version $c$
of the partition along with a path $\pi$ comprising the identity of
\processes that forwarded the corresponding $\alpha$ message. Such a
$\delta_{s, c}^{\pi}$ message implements the uncertain $\delta?$
message of Figure~\ref{fig:proofB}. It fulfils the double role of
removing stale control information without modifying the local counter
of the source (since the partition may still exist), and removing
loops to ensure termination (since \processes do not modify their
local state to reflect such a delivery, messages piggyback
monotonically such increasing control information).

@@

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the
shortest path of one of involved \processes plus downstream
\processes. As a side effect, removing an edge may also impair the
propagation of a partition delete. To implement this behavior, \NAME
uses its implementation of $\delta?$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.

>>>>

\begin{theorem}[\label{theo:dcp}BEF$^+$: BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
ensure consistent partitioning, best eventual forwarding (see
Theorem~\ref{theo:bef}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item then best eventual forwarding so such an $m'$ ends up
  originating from the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then BEF:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every \process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \process eventually
    delivers and forwards the best up-to-date delivered messages.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  By using BEF along with purge of stale messages that triggers BEF,
  \processes reach consistent partitioning together as in
  Theorem~\ref{theo:bef}.
\end{proof}

%% Figure removed as it's kind of redundant with preceding figure that
%% depicts the issue
%% \begin{figure} 
%%   \centering\input{input/figproofA.tex}
%%   \caption{\label{fig:proofA}Stale $\alpha$ messages may
%%       stop other $\alpha$ messages from reaching all \processes ($b$
%%       and $c$) that require it along the shortest path. Consistent
%%       partitioning requires eventual purging of stale messages (see
%%       Figure~\ref{fig:proofB}).}
%% \end{figure}

The main challenge consists in implementing a purging mechanism that
ensures the \emph{eventual and definitive} removal of stale control
information. One could guarantee consistent partitioning by always
propagating the $\delta$ messages corresponding to the $\alpha$
messages it propagated before. In Figure~\ref{fig:problem}, it means
that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
its neighbors \Process~$c$ and \Process~$d$ may need the notification
of removal $\delta_a$ if it exists. However, such a solution also
implies that \processes generate traffic not only related to their
current partition, but also related to partitions they belonged to in
the past. This would prove overly expensive in dynamic systems where
\processes join and leave the system, create and delete partitions, at
any time.  Instead, we propose to use the delivery order at each
\process to detect possible inconsistencies and solve them.
%% Together, \processes eventually remove all stale control information
%% (transiting messages and local states) of the system leaving room for
%% propagation of messages about up-to-date partitions.

@@

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  Purging stale control information from its source to every \process
  that may have delivered it last requires three phases:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

\begin{figure}
  \centering\input{input/figproofB.tex}
  \caption{\label{fig:proofB}Stale $\alpha$ messages may stop $\delta$
    messages from reaching \processes with the corresponding
    partition. Consistent partitioning requires that all \processes
    propagate $\delta$ messages as often as possible (I); detect
    possible inconsistencies when parents' $\alpha$ messages
    contradict history or state (II); notify \processes of possible
    inconsistencies (III).}
\end{figure}

\begin{proof}
  Figure~\ref{fig:proofB} depicts all possible cases that need
  appropriate purging. A chain of \processes $[a, b, c, d]$ delivered
  and forwarded a message $\alpha_a$. Some \processes may have
  delivered messages about other partitions before or after
  $\alpha_a$.
  \begin{asparadesc}
  \item [\processes with last $\alpha_a$:] \Processes such as
    \Process~$a$ where the last and best partition is still $P_a$. By
    propagating from \process to \process the corresponding $\delta_a$
    message, these \processes purge $\alpha_a$.
  \item [\processes with $\alpha_a^y \rightarrow \alpha_e^z$ with last
    $\alpha_e^z$, for $\alpha_e^z < \alpha_a^y$:] \Processes such as
    \Process~$e$ that do not directly suffer from the non-delivery of
    $\delta_a$. They need to purge their own $P_e$ if need
    be. Nonetheless, they deliver and forward $\alpha_e$ that at least
    one following \process will receive.
  \item [\processes with $\delta_e \rightarrow \alpha_d$:] \Processes
    such as \Process~$f$ that do not belong to the preceding category,
    for they already delivered $\delta_e$. Nevertheless, best eventual
    forwarding guarantees that they receive $\alpha_e$, which
    contradicts their history or state. In such a case, the detecting
    \processes purge their own $\alpha_a$. The detecting \processes
    must also notify subsequent \processes that their current
    partition \emph{may be} deleted. Indeed their parent may have
    blocked the corresponding $\delta$ messages and subsequent
    \processes must purge their possibly stale state, for the sake of
    consistency.  We note such a notification $\Delta_a$ to emphasize
    the uncertainty of a $\delta$ message.
  \item [\processes with last $\alpha_a$ receiving $\Delta_a$ from
    their parent:] \Processes such as \Process~$g$ that have
    $\alpha_a$ but preceding delivered messages are not
    important. Such \processes must trust detecting \processes by
    delivering and forwarding $\Delta_a$. It is worth noting that
    these messages are subject to all aforementioned blocking
    conditions, but are also solved by aforementioned mechanisms.
  \end{asparadesc}

@@

This vector of versions constitutes a summary of deliveries. \NAME
uses it to detect possible inconsistent partitioning as depicted in
Figure~\ref{fig:proofB}. A detecting \process then propagates a
$\delta$ message conveying the unique identifier $s$ and version $c$
of the partition along with a path $\pi$ comprising the identity of
\processes that forwarded the corresponding $\alpha$ message. Such a
$\delta_{s, c}^{\pi}$ message implements the uncertain $\Delta$
message of Figure~\ref{fig:proofB}. It fulfils the double role of
removing stale control information without modifying the local counter
of the source (since the partition may still exist), and removing
loops to ensure termination (since \processes do not modify their
local state to reflect such a delivery, messages piggyback
monotonically such increasing control information).

@@

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the shortest
path of one of involved \processes plus downstream \processes. As a
side effect, removing an edge may also impair the propagation of a
partition delete. To implement this behavior, \NAME uses its
implementation of $\Delta$ messages. This prove costly but enables
\NAME even in dynamic networks subject to physical partitioning.
